%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerlastnamestyle{Angie Paola} \headerfirstnamestyle{Manrique Ravelo} \\
	\vspace{2mm}
	{\hspace{0.8cm}\faEnvelope\ angie27manrique@gmail.com}  |  {\faMobile\ (+57) 3107669063}  |  {\faMapMarker\ Bogotá, Colombia} 
	\newline {\faLink\ \href{https://www.linkedin.com/in/angie27manrique/}{https://www.linkedin.com/in/angie27manrique/}}
\end{center}

\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Languages:  & {\skill{ Java, C\#, TypeScript, SQL, Python (Beginner).}} \\
		Frameworks:  & {\skill{ Spring, Angular.}} \\
		Databases:  & {\skill{ PostgreSQL, MySQL, SQLServer, MongoDB.}} \\
		Cloud:  & {\skill{ AWS, Azure.}} \\
		Technologies / Tools: \hspace{0.05cm} & {\skill{ Docker, Jenkins, GraphQL, Kafka, SonarQube, Maven, npm, Git.}} \\
		Practices:  & {\skill{ Agile, Scrum, SOLID Principles, Test-Driven Development, Code Reviews.}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}
\vspace{-7mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Backend Engineer Semisenior}
	{Crehana}
	{Bogotá, Colombia}
	{Feb. 2021 – Jun. 2024}
	{\begin{cvitems}
		\vspace{0.5mm}
		\item {Developed innovative software modules using Java and Spring Framework, ensuring data integrity and resulting in multiple recurring functionalities for 1,000,000+ customer transactions.}
		\item {Coded 10+ interactive features in Angular, enhancing platform functionality; integration resulted in 15\% increase in user engagement and the tool is now used by over 200,000 active users.}
		\item {Significantly improved reporting dashboard performance by identifying and eliminating bottlenecks, resulting in a 50\% reduction in load time.}
		\item {Designed and built RESTful APIs, improving system integration and data accessibility.}
		\end{cvitems}}

	\cventry
	{Web Designer}
	{Ink digital}
	{Bogotá, Colombia}
	{Nov. 2020 – Jan. 2021}
	{\begin{cvitems}
		\vspace{0.5mm}
		\item {Constructed innovative and high-quality designs that consistently scored above 90\% in performance and accessibility benchmarks.}
		\item {Developed client websites using the WordPress CMS, resulting in an average page load time of 3 seconds or less.}
		\item {Used Google Ads to position websites, leading to a 15\% increase in organic traffic.}
		\end{cvitems}}

	\cventry
	{Developer and Co-Investigator}
	{Universidad de Cundinamarca}
	{Facatativá, Colombia}
	{Nov. 2019 – Dec. 2020}
	{\begin{cvitems}
		\vspace{0.5mm}
		\item {Created and deployed a web application to visualize the graphical results of descriptive and predictive analyses using data mining techniques.}
		\item {Conducted a comprehensive analysis of ICFES data, resulting in the creation of 10 key indicators to measure gender disparities in Colombian education.}
		\item {Presented research findings at 3 national conferences between 2019 and 2020.}
		\end{cvitems}}
\end{cventries}


\cvsection{Projects}
\begin{cventries}
	\vspace{2mm}
	\cventry
	{}
	{AquaFeeder: Real-Time Fish Detection and Feeding Optimization System \vspace{-5mm}}
	{MATLAB, Arduino, Computer Vision \vspace{-5mm}}
	{}
	{\begin{cvsectionnormaltext}
		\item{Developed a smart system using real-time webcam, MATLAB, and Arduino to detect fish species and predict their length and food portions. }
	\end{cvsectionnormaltext}}	
	
	\vspace{-3mm}
	\cventry
	{}
	{Gender Gaps in STEM fields in the Saber 2016 Tests in Colombia \vspace{-5mm}}
	{Revista Pensamiento Udecino \vspace{-5mm}}
	{Nov 6, 2020 \vspace{-5mm}}
	{\begin{cvsectionnormaltext}
		\item{Published research article analyzing gender disparities in Colombian higher education. 
		\newline \faLink\ \href{https://revistas.ucundinamarca.edu.co/index.php/Pensamiento_udecino/article/view/79}{https://revistas.ucundinamarca.edu.co/index.php/Pensamiento\_udecino/article/view/79}}
	\end{cvsectionnormaltext}}
	
	\vspace{-5mm}
	
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{8mm}
\cvsection{Education}
\begin{cventries}
	\vspace{-3mm}
	\cventry
	{}
	{Universidad de Cundinamarca \vspace{-5mm}}
	{Facatativá, Colombia \vspace{-5mm}}
	{Feb 2016 – Mar 2021 \vspace{-5mm}}
	{\begin{cvsectionnormaltext} 
		\item{Bachelor's Degree in Systems Engineering}
	\end{cvsectionnormaltext}}
\end{cventries}

\end{document}